### 2024-03-20 paper/main.tex
added supplementary
new updates with math

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
% \usepackage[backend=biber]{biblatex}
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
\usepackage{fontspec} %XeLatex
\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
% \definecolor{myudblue}{RGB}{0, 83, 159}
\begin{document}
HELLOOOOOOOOO

aw;lesfajfp 8uyf

% \begin{figure}
%     \centering
%     \includegraphics{/figures/test.png}
% \end{figure}

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
\usepackage{float}
\usepackage{caption}
\graphicspath{ {./figures/} }
\usepackage[backend=biber]{biblatex}
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
\usepackage{fontspec} %XeLatex
\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
% Set caption styles
% \DeclareCaptionLabelFormat{table}{1-2}
\captionsetup[table]{labelfont=bf,labelsep=period}
\captionsetup[figure]{labelfont=bf,labelsep=period}

\newcommand{\SethCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{black}{#1}}\normalsize }

% \definecolor{myudblue}{RGB}{0, 83, 159}
\begin{document}
% \SectionHeader{Main Figures}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figures/exp1_experimental_design.png}

%     \SethCaption{Figure 1.}{Experimental Design}
% \end{figure}
% \begin{figure}[H]
%     \centering
%     \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}

%     \SethCaption{Figure 2.}{Data}
% \end{figure}
% \begin{figure}[H]
%     \centering
%     \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}

%     \SethCaption{Figure 3.}{Data}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale = 1]{figures/model_diagram.png}

%     \SethCaption{Figure 4.}{Data}
% \end{figure}
% \begin{figure}[H]
%     \centering
%     \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}

%     \SethCaption{Figure 5.}{Data w/ models}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale = 1]{figures/exp2_design.png}

%     \SethCaption{Figure 6.}{Experiment 2 Design}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale = 1]{figures/exp2_reaction_panel.png}

%     \SethCaption{Figure 7.}{React or Guess panel}
% \end{figure}

% \SectionHeader{Supplementary Figures}

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale = 1]{figures/reaction_guess_decisions.png}

%     \SethCaption{Supplementary Figure 1.}{Reaction and Guess Decisions}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale = 1]{figures/model_losses.png}

%     \SethCaption{Supplementary Figure 2.}{Model Loss Comparison}
% \end{figure}

\SectionHeader{Methods}
\begin{table}[h]
    \centering
    \begin{tabular}{|l | c|}
        \hline
        Agent Movement Onset Time Mean        & $\mu_{A}$         \\
        Agent Movement Onset Time Uncertainty & $\sigma_{A}$      \\
        Reaction Time Mean                    & $\mu_{RT}$        \\
        Reaction Time Uncertainty             & $\sigma_{RT}$     \\
        Movement Time Mean                    & $\mu_{MT}$        \\
        Movement Time Uncertainty             & $\sigma_{MT}$     \\
        Neuromechanical Delay Mean            & $\mu_{NMD}$       \\
        Neuromechanical Delay Uncertainty     & $\sigma_{NMD}$    \\
        Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
        Switch Time Mean                      & $\mu_{switch}$    \\
        Switch Time Uncertainty               & $\sigma_{switch}$ \\
        \hline
    \end{tabular}
    \caption[]{Inputs to the model}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{|l | c|}
        \hline
        Reaction Time Delay       & $\mathcal{N}(\mu_{RT},\sigma_{RT})$         \\
        Movement Time Delay       & $\mathcal{N}(\mu_{MT},\sigma_{MT})$         \\
        Neuromechanical Delay     & $\mathcal{N}(\mu_{NMD},\sigma_{NMD})$       \\
        Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
        Switch Time Delay         & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
        \hline
    \end{tabular}
    \caption[]{Inputs to the model}
\end{table}

% Define pdf and cdf
\begin{equation}
    f(t) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{t-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    F(t) = P(T\leq t) = \int_{-\infty}^{t} f(t)dt
\end{equation}
\begin{equation}
    t \in [0,1500]
\end{equation}
\begin{equation}
    T\sim\mathcal{N}(\mu,\sigma)
\end{equation}

% Define prob react and guess
\begin{equation}
    P(React|\tau) = P(\tau>\mu_{A}; \sigma_{tau}, \sigma_{A})
\end{equation}
\begin{equation}
    P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{tau}, \sigma_{A})
\end{equation}

% Define expected value
\begin{equation}
    \mu_{X} = \sum_{i = -\infty}^{\infty}x_{i}f(x_{i};\mu_{X}, \sigma_{X})
\end{equation}

% Define indicator function
\begin{equation}
    \mathbbm{1}_{a_{i},t_{i} \in S} = 
    \begin{cases}
        1, & \text{if } a_{i},t_{i} \in S \\
        0, & \text{if }  a_{i},t_{i} \notin S
    \end{cases}    
\end{equation}

% Define

% Movement Onset times
\begin{equation}
    \mu_{RMO} = \mu_{A_{cutoff}} + \mu_{RT}
\end{equation}
\begin{equation}
    \sigma_{RMO} = \sqrt{\sigma_{A_{cutoff}}^2 + \sigma_{RT}^2}
\end{equation}
\begin{equation}
    \mu_{GMO} = \\tau +  \mu_{NMD} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{GMO} = \sqrt{\sigma_{\tau}^2 + \sigma_{NMD}^2 + \sigma_{switch}^2}
\end{equation}

% Scores

\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}
